Testing Education State Transitions

### 2023-06-15 minos/testing/education_transitions.Rmd
WIP trying to figure out how many people transition into different education levels and at what age
Added some chunks to investigate the ages at which people achieve certain education levels, and the mean age for each level

>>>>

```{r}
raw <- raw.dat %>%
  select(pidp, time, age, education_state) %>%
  arrange(pidp, time) %>%
  group_by(pidp) %>%
  mutate(levelUp = ifelse(education_state != dplyr::lag(education_state, order_by=time), TRUE, FALSE)) %>%
  filter(!is.na(levelUp)) %>%
  filter(levelUp == TRUE)

ggplot(data = filter(raw, education_state == 2), aes(x = age)) +
  geom_histogram() +
  labs(title = 'Education State == 2')

ggplot(data = filter(raw, education_state == 3), aes(x = age)) +
  geom_histogram() +
  labs(title = 'Education State == 3')

ggplot(data = filter(raw, education_state == 5), aes(x = age)) +
  geom_histogram() +
  labs(title = 'Education State == 5')

ggplot(data = filter(raw, education_state == 6), aes(x = age)) +
  geom_histogram() +
  labs(title = 'Education State == 6')

ggplot(data = filter(raw, education_state == 7), aes(x = age)) +
  geom_histogram() +
  labs(title = 'Education State == 7')

raw$education_state <- factor(raw$education_state)

ggplot(data = raw, aes(x = age, group = education_state, fill = education_state)) +
  geom_histogram()
  labs(title = 'Education state')
